Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/WSSSPE3_review.tex
new language for old point in keynote
Jeffrey Carver's talk

Turk said that sustaining scientific software really meant to him conducting
scientific inquiries, often by some specific software, and sustaining the people
we care about, our careers, and the future of our fields. According to Turk, we
all have an invested stake in sustaining scientific software. Hence, having
``sustained'' projects can suffocate new projects, for which we need to keep a
lookout.
%This is a straw man concept, but it's something to look out for, since organizations will act in their own interest.

@@

>>>>

Turk said that sustaining scientific software really meant to him conducting
scientific inquiries, often by some specific software, and sustaining the people
we care about, our careers, and the future of our fields. According to Turk, we
all have an invested stake in sustaining scientific software. Hence, having
``sustained'' projects can suffocate new projects, so we need to make sure
we don't cause novel ideas and packages to suffer at the hands of the status quo.
%This is a straw man concept, but it's something to look out for, since organizations will act in their own interest.

@@

I argue that for scientific software to be truly sustainable, there is a need
for developers to use appropriate software engineering practices. My experience
interacting with scientific teams indicates that choosing and tailoring these
practices is not a trivial exercise. There is a general culture clash between
software engineering and science that hinders our ability to communicate and
choose appropriate methods. In addition, many experience scientific software
developers appear to be unaware of software engineering practices that may be
beneficial to them. The most appropriate software engineering practices are
those that are lightweight, properly tailored, and focus on the key software
development problems faced by scientists. In order to increase the use of
software engineering in science, we need more documented success stories. These
successes need to be socialized within the scientific community through
workshops like the Software Engineering for Science workshop
series~\footnote{\href{http://www.SE4Science.org/workshops}{http://www.SE4Science.org/workshops}}
and the new Software Engineering track in
Computing in Science and Engineering magazine.
